A systematic search for transiting planets in the \KT\ data

### 2015-02-13 ms.tex
intro tweaks

The alternative to this approach is to \emph{simultaneously fit} both the systematics
and the transit signals.
Simultaneous fitting can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, it permits us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties about the systematic effects
to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}

In this \paper\ we present a data-analysis technique for exoplanet search and
characterization that is insensitive to spacecraft-induced trends in the light
curves.
We assume that the trends in the observed light curves in each star due to
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of a
huge number of these basis vectors and a transit model.
Our method builds on the ideas of previous data-driven de-trending procedures
like Pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2} but we can use a
much more flexible systematics model without worrying about over-fitting.

@@

Catalogs of transiting planets found in the \KT\ data will be important to
better understand the physical properties, formation, and evolution of
planetary systems.
These planets, especially when they orbit especially bright or late-type
stars, will be useful targets for ground-based and space-based follow-up, both
for current facilities and those planned in the near-future such as \jwst.
They will also deliver input data for next-generation population inferences
\citep{dfm}, especially for the population of planets around cool stars
\citep[for example][]{dressing}.

>>>>

The alternative to this approach is to \emph{simultaneously fit} both the systematics
and the transit signals.
Simultaneous fitting can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, it permits us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties about the systematic effects
to our confidence in the detection.
This marginalization ensures that any conclusions we come to about the exoplanet
properties are conservative, given the freedom of the systematics model.

In this \paper\ we present a data-analysis technique for exoplanet search and
characterization that is insensitive to spacecraft-induced trends in the light
curves.
We assume that the trends in the observed light curves in each star due to
spacecraft motion are shared by other stars; the systematic effects are
modeled as sums of stars.
We reduce the dimensionality by running PCA on stellar light curves
to obtain the dominant modes.
The search for planets proceeds by modeling the data as a linear combination of
150 of these basis vectors and a transit model.
Our method builds on the ideas behind previous data-driven de-trending procedures
such as the \kepler\ pipeline pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2},
but (because of our simultaneous fitting approach) we can use a
much more flexible systematics model without worrying about over-fitting.

@@

Catalogs of transiting planets found in the \KT\ data will be important to
better understand the physical properties, formation, and evolution of
planetary systems.
These planets, especially when they orbit bright or late-type
stars, will be useful targets for ground-based and space-based follow-up, both
for current facilities and those planned in the near future such as \jwst.
They will also deliver input data for next-generation population inferences
\citep{dfm}, especially for the population of planets around cool stars
\citep[for example,][]{dressing}.
